Proposed Solution

### 2016-11-14 Ennan-Proposal/travis.tex
autocommit

@@

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
    \draw (0,0) rectangle (6,4); 
    \node [align=left] at (1.5,3.2) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
    \draw (1.5,0.2) rectangle (5,2.2);
    \node [align=left] at (3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
  \end{tikzpicture}
  \caption{An example set of necessary and breaking rules if we have seen a failing file with {\footnotesize node\_js: 0}, and a passing file with {\footnotesize node\_js: 0.4.}}
  \label{fig:versionSL}
\end{figure}

>>>>

\begin{wrapfigure}{l}{0.5\textwidth}
  \includegraphics[width=0.45\textwidth]{figs/Version_space}
  \caption{\small Red circles are failing files, and green pluses are passing files.}
  \label{fig:versionSL}
\end{wrapfigure}

@@

Figure~\ref{fig:versionSL} shows an example set of necessary and breaking rules that would be learn if the training set contains a failing file with {\small node\_js: 0}, and a passing file with {\small node\_js: 0.4.}
The breaking rules will describe the conditions for an incorrect file based on examples we have seen of incorrect files (red circles).
Likewise, the necessary rules will describe the conditions for a correct file based on examples we have seen of correct files (green pluses).
This results in a space (green stripes) where a file may contain relations that cannot be classified as either breaking or necessary.
Part of the research task will be to find an optimal treatment for such cases.
